---
title: "project2"
output: html_document
date: "2024-10-23"
---
```{r}
library(tidyverse)
library(arrow)
library(RSQLite)
library(tidymodels)
library(butcher)
library(future)
library(tidyfinance) # for portfolio sorts
library(data.table)
```

Data preparation
```{r}
characteristics <- fread("GKX_20201231.csv")
characteristics <- characteristics |>
  rename(month = DATE) |>
  mutate(
    month = ymd(month),
    month = floor_date(month, "month")
  ) |>
  rename_with(~ paste0("characteristic_", .), 
              -c(permno, month, sic2,RET))

characteristics <- characteristics |>
  drop_na(sic2) |>
  mutate(sic2 = as_factor(sic2))
```

cross-sectional ranking
```{r}
rank_transform <- function(x) {
  rank_x <- rank(x)
  rank_x[is.na(x)] <- NA
  min_rank <- 1
  max_rank <- length(na.omit(x))
  
  if (max_rank == 0) { # only NAs
    return(rep(NA, length(x)))    
  } else {
    return(2 * ((rank_x - min_rank) / (max_rank - min_rank) - 0.5)) 
  }
}

characteristics <- characteristics |>
  group_by(month) |>
  mutate(across(contains("characteristic"), rank_transform)) |>
  ungroup()
```

deal with missing characteristics
```{r}
characteristics <- characteristics |>
  group_by(month) |> 
  mutate(across(contains("characteristic"), 
                \(x) replace_na(x, median(x, na.rm = TRUE)))) |> 
  ungroup()

characteristics <- characteristics |>
  mutate(across(contains("characteristic"), 
                \(x) replace_na(x, 0)))
```

Macroeconomic Predictors and make them into SQL
```{r}
library(tidyverse)
library(tidyfinance)
library(scales)
library(RSQLite)
library(dbplyr)
start_date <- ymd("1957-03-01")
end_date <- ymd("2021-01-01")
sheet_id <- "1bM7vCWd3WOt95Sf9qjLPZjoiafgF_8EG"
sheet_name <- "Monthly"
macro_predictors_url <- paste0(
  "https://docs.google.com/spreadsheets/d/", sheet_id,
  "/gviz/tq?tqx=out:csv&sheet=", sheet_name
)
macro_predictors_raw <- read_csv(macro_predictors_url)
macro_predictors <- macro_predictors_raw |>
  mutate(date = ym(yyyymm)) |>
  mutate(across(where(is.character), as.numeric)) |>
  mutate(
    IndexDiv = Index + D12,
    logret = log(IndexDiv) - log(lag(IndexDiv)),
    Rfree = log(Rfree + 1),
    rp_div = lead(logret - Rfree, 1), # Future excess market return
    dp = log(D12) - log(Index), # Dividend Price ratio
    dy = log(D12) - log(lag(Index)), # Dividend yield
    ep = log(E12) - log(Index), # Earnings price ratio
    de = log(D12) - log(E12), # Dividend payout ratio
    tms = lty - tbl, # Term spread
    dfy = BAA - AAA # Default yield spread
  ) |>
  rename(month = date) |>
  select(
    month, rp_div, dp, dy, ep, de, svar,
    bm = `b/m`, ntis, tbl, lty, ltr,
    tms, dfy, infl
  ) |>
  filter(month >= start_date & month <= end_date) |>
  drop_na()
dataset <- dbConnect(
  SQLite(),
  "dataset.sqlite",
  extended_types = TRUE
)
dbWriteTable(
  dataset,
  "macro_predictors",
  value = macro_predictors,
  overwrite = TRUE
)

```

merge them all
```{r}
dataset <- dbConnect(SQLite(), 
                          "dataset.sqlite",
                          extended_types = TRUE)



macro_predictors <- tbl(dataset, "macro_predictors") |>
  select(month, dp, ep, bm, ntis, tbl, tms, dfy, svar) |>
  collect() |>
  rename_with(~ paste0("macro_", .), -month)

macro_predictors <- macro_predictors |>
  select(month) |>
  left_join(macro_predictors |> mutate(month = month %m+% months(1)), 
            join_by(month))

characteristics <- characteristics |>
  inner_join(macro_predictors, join_by(month)) |>
  arrange(month, permno) |>
  mutate(macro_intercept = 1) |>
  select(permno, month, RET,
         sic2, contains("macro"), contains("characteristic"))
```

Creat dataset with all interaction terms
The total number of covariates is 94×(8+1)+74=920
I process my data year-by-year and store each portion separately to efficiently handle memory.
```{r}
library(dplyr)
library(recipes)
library(arrow)

# Assume characteristics contains a column called 'year'
characteristics <- characteristics |> mutate(year = year(month))

# Create a function to process data for a single year
process_and_save_year <- function(year_data, year) {
  rec <- recipe(RET ~ ., data = year_data) |>
    update_role(permno, month, new_role = "id") |>
    step_interact(terms = ~ contains("characteristic"):contains("macro"), keep_original_cols = FALSE) |>
    step_dummy(sic2, one_hot = TRUE)
  
  rec <- prep(rec)
  baked_data <- bake(rec, new_data = year_data)
  
  # Store the processed data in Parquet format
  write_parquet(baked_data, paste0("characteristics_", year, ".parquet"))
}

# Process each year separately
unique_years <- unique(characteristics$year)
for (year in unique_years) {
  year_data <- characteristics |> filter(year == !!year)
  process_and_save_year(year_data, year)
}
```

Sample splitting and tuning
```{r}
validation_length <- 12

estimation_periods <- tibble(testing_year = 1987:2021,
                             validation_end = testing_year - 1,
                             validation_start = testing_year - validation_length,
                             training_start = 1957,
                             training_end = validation_start - 1) |>
  select(contains("training"), validation_start, validation_end, testing_year)

visualization_data = pmap_dfr(estimation_periods, 
                              \(training_start, 
                                training_end, 
                                validation_start, 
                                validation_end, 
                                testing_year){
  tibble(year = 1957:2021,
         classification = case_when(year >= training_start & year <= training_end ~ "Training",
                                    year >= validation_start & year <= validation_end ~ "Validation",
                                    year == testing_year ~ "testing"), 
         testing_year)
  }) |> 
  drop_na()

ggplot(visualization_data, 
       aes(x = year, y = testing_year, color = classification)) +
  geom_point(size = 1) +
  labs(title = "Data classification timeline",
       x = NULL, y = NULL, color = NULL) +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
```

OLS +H
```{r}
# Load h2o package
library(h2o)
library(arrow)
h2o.init()

# Use "./" to specify the current directory
file_paths <- list.files(path = "./", pattern = "\\.parquet$", full.names = TRUE)

# Initialize an empty list to store the R^2 values and observation counts for each file
r2_list <- list()
counts <- c()

# Iterate over each file, process the data, and store the results
for (file_path in file_paths) {
  
  # Load data from the current file
  data <- read_parquet(file_path)
  h2o_data <- as.h2o(data)
  
  # Define the response variable and predictor variables
  y <- "RET"
  x <- setdiff(names(data), y)
  
  # Perform OLS regression using h2o.glm()
  model <- h2o.glm(x = x, y = y, training_frame = h2o_data, family = "gaussian")
  
  # Calculate the R^2 for the current subset
  performance <- h2o.performance(model, newdata = h2o_data)
  r2 <- h2o.r2(performance)
  
  # Store the R^2 and observation count for the current file for weighted calculation
  r2_list[[file_path]] <- r2
  counts <- c(counts, nrow(data))
  
  # Clean up memory
  h2o.rm(h2o_data)
}

# Calculate weighted R^2
overall_r2 <- sum(unlist(r2_list) * counts) / sum(counts)
print(paste("Overall R^2:", overall_r2))

# Shut down h2o
h2o.shutdown(prompt = FALSE)



```

OLS_3 +H
```{r}
# Load necessary libraries
library(h2o)
library(arrow)
h2o.init()

# Use "./" to specify the current directory containing Parquet files
file_paths <- list.files(path = "./", pattern = "\\.parquet$", full.names = TRUE)

# Initialize lists to store R^2 values and observation counts for each file
r2_list <- list()
counts <- c()

# Loop through each file, process data, and store results
for (file_path in file_paths) {
  
  # Load data for the current file
  data <- read_parquet(file_path)
  
  # Select only the required variables
  data <- data[, c("RET", "characteristic_mvel1_x_macro_dp","characteristic_mvel1_x_macro_ep","characteristic_mvel1_x_macro_bm","characteristic_mvel1_x_macro_ntis",
 "characteristic_mvel1_x_macro_tbl","characteristic_mvel1_x_macro_tms","characteristic_mvel1_x_macro_dfy","characteristic_mvel1_x_macro_svar","characteristic_bm_x_macro_dp","characteristic_bm_x_macro_ep","characteristic_bm_x_macro_bm","characteristic_bm_x_macro_ntis","characteristic_bm_x_macro_tbl","characteristic_bm_x_macro_tms","characteristic_bm_x_macro_dfy","characteristic_bm_x_macro_svar","characteristic_mom1m_x_macro_dp","characteristic_mom1m_x_macro_ep","characteristic_mom1m_x_macro_ntis","characteristic_mom1m_x_macro_tbl","characteristic_mom1m_x_macro_tms","characteristic_mom1m_x_macro_dfy","characteristic_mom1m_x_macro_svar","characteristic_mom1m_x_macro_bm")]
  
  # Upload selected data to the h2o cluster
  h2o_data <- as.h2o(data)
  
  # Define response variable and predictor variables
  y <- "RET"
  x <- c("characteristic_mvel1_x_macro_dp","characteristic_mvel1_x_macro_ep","characteristic_mvel1_x_macro_bm","characteristic_mvel1_x_macro_ntis",
 "characteristic_mvel1_x_macro_tbl","characteristic_mvel1_x_macro_tms","characteristic_mvel1_x_macro_dfy","characteristic_mvel1_x_macro_svar","characteristic_bm_x_macro_dp","characteristic_bm_x_macro_ep","characteristic_bm_x_macro_bm","characteristic_bm_x_macro_ntis","characteristic_bm_x_macro_tbl","characteristic_bm_x_macro_tms","characteristic_bm_x_macro_dfy","characteristic_bm_x_macro_svar","characteristic_mom1m_x_macro_dp","characteristic_mom1m_x_macro_ep","characteristic_mom1m_x_macro_ntis","characteristic_mom1m_x_macro_tbl","characteristic_mom1m_x_macro_tms","characteristic_mom1m_x_macro_dfy","characteristic_mom1m_x_macro_svar","characteristic_mom1m_x_macro_bm")
  
  # Perform OLS regression using h2o.glm with only selected predictors
  model <- h2o.glm(x = x, y = y, training_frame = h2o_data, family = "gaussian")
  
  # Calculate R^2 for the current subset
  performance <- h2o.performance(model, newdata = h2o_data)
  r2 <- h2o.r2(performance)
  
  # Store the R^2 and the number of observations for weighting
  r2_list[[file_path]] <- r2
  counts <- c(counts, nrow(data))
  
  # Clean up to free memory
  h2o.rm(h2o_data)
}

# Calculate weighted R^2
overall_r2 <- sum(unlist(r2_list) * counts) / sum(counts)
print(paste("Overall R^2:", overall_r2))

# Shut down h2o
h2o.shutdown(prompt = FALSE)


```


Elastic Net with Huber Loss +H
```{r}
# Load necessary libraries
library(h2o)
library(arrow)
h2o.init()

# Use "./" to specify the current directory containing Parquet files
file_paths <- list.files(path = "./", pattern = "\\.parquet$", full.names = TRUE)

# Initialize lists to store R^2 values and observation counts for each file
r2_list <- list()
counts <- c()

# Loop through each file, process data, and store results
for (file_path in file_paths) {
  
  # Load data for the current file
  data <- read_parquet(file_path)
  
  # Upload data to the h2o cluster
  h2o_data <- as.h2o(data)
  
  # Define response variable and automatically select predictor variables
  y <- "RET"
  x <- setdiff(names(data), y)  # All columns except RET as predictors
  
  # Perform Elastic Net with Huber loss using h2o.deeplearning()
  model <- h2o.deeplearning(x = x, y = y, training_frame = h2o_data,
                            activation = "Rectifier",       # Simple activation function
                            hidden = c(50, 50),             # Hidden layer structure
                            epochs = 3,                     # Fewer training epochs
                            loss = "Huber",                 # Use Huber loss
                            huber_alpha = 0.9,              # Controls sensitivity of Huber loss
                            l1 = 0.5,                       # Elastic Net mixing parameter for L1 regularization
                            l2 = 0.5)                       # Elastic Net mixing parameter for L2 regularization
  
  # Calculate R^2 for the current subset
  performance <- h2o.performance(model, newdata = h2o_data)
  r2 <- h2o.r2(performance)
  
  # Store the R^2 and the number of observations for weighting
  r2_list[[file_path]] <- r2
  counts <- c(counts, nrow(data))
  
  # Clean up to free memory
  h2o.rm(h2o_data)
}

# Calculate weighted R^2
overall_r2 <- sum(unlist(r2_list) * counts) / sum(counts)
print(paste("Overall R^2:", overall_r2))

# Shut down h2o
h2o.shutdown(prompt = FALSE)

```

GLM +H with group loss
```{r}
# Load necessary libraries
library(h2o)
library(arrow)
h2o.init()

# Use "./" to specify the current directory containing Parquet files
file_paths <- list.files(path = "./", pattern = "\\.parquet$", full.names = TRUE)

# Initialize lists to store R^2 values and observation counts for each file
r2_list <- list()
counts <- c()

# Loop through each file, process data, and store results
for (file_path in file_paths) {
  
  # Load data for the current file
  data <- read_parquet(file_path)
  
  # Upload data to the h2o cluster
  h2o_data <- as.h2o(data)
  
  # Define response variable and automatically select predictor variables
  y <- "RET"
  x <- setdiff(names(data), y)  # All columns except RET as predictors
  
  # Perform GLM with group lasso using h2o.glm
  model <- h2o.glm(x = x, y = y, training_frame = h2o_data,
                   family = "gaussian",       # For linear regression
                   alpha = 1,                 # L1 penalty for group lasso
                   lambda_search = TRUE)      # Automatically search for the best lambda
  
  # Calculate R^2 for the current subset
  performance <- h2o.performance(model, newdata = h2o_data)
  r2 <- h2o.r2(performance)
  
  # Store the R^2 and the number of observations for weighting
  r2_list[[file_path]] <- r2
  counts <- c(counts, nrow(data))
  
  # Clean up to free memory
  h2o.rm(h2o_data)
}

# Calculate weighted R^2
overall_r2 <- sum(unlist(r2_list) * counts) / sum(counts)
print(paste("Overall R^2:", overall_r2))

# Shut down h2o
h2o.shutdown(prompt = FALSE)

```

random forest
```{r}
# Load necessary libraries
library(h2o)
library(arrow)
h2o.init()

# Use "./" to specify the current directory containing Parquet files
file_paths <- list.files(path = "./", pattern = "\\.parquet$", full.names = TRUE)

# Initialize lists to store R^2 values and observation counts for each file
r2_list <- list()
counts <- c()

# Loop through each file, process data, and store results
for (file_path in file_paths) {
  
  # Load data for the current file
  data <- read_parquet(file_path)
  
  # Upload data to the h2o cluster
  h2o_data <- as.h2o(data)
  
  # Define response variable and automatically select predictor variables
  y <- "RET"
  x <- setdiff(names(data), y)  # All columns except RET as predictors
  
  # Train Random Forest model with optimized parameters for faster runtime
  model <- h2o.randomForest(x = x, y = y, training_frame = h2o_data,
                            ntrees = 50,           # Reduced number of trees
                            max_depth = 10,        # Reduced max depth
                            sample_rate = 0.8,     # Use 80% of data for each tree
                            seed = 1234)           # For reproducibility
  
  # Calculate R^2 for the current subset
  performance <- h2o.performance(model, newdata = h2o_data)
  r2 <- h2o.r2(performance)
  
  # Store the R^2 and the number of observations for weighting
  r2_list[[file_path]] <- r2
  counts <- c(counts, nrow(data))
  
  # Clean up to free memory
  h2o.rm(h2o_data)
}

# Calculate weighted R^2
overall_r2 <- sum(unlist(r2_list) * counts) / sum(counts)
print(paste("Overall R^2:", overall_r2))

# Shut down h2o
h2o.shutdown(prompt = FALSE)

```

PLS
```{r}
# Load necessary libraries
library(arrow)
library(pls)

# Specify the current directory containing Parquet files
file_paths <- list.files(path = "./", pattern = "\\.parquet$", full.names = TRUE)

# Initialize lists to store R^2 values and observation counts for each month and year
monthly_pls_r2_list <- list()
monthly_counts <- list()
annual_pls_r2_list <- list()
annual_counts <- list()

# Loop through each file, process data, and store results
for (file_path in file_paths) {
  
  # Load data for the current file
  data <- read_parquet(file_path)
  
  # Check for required columns
  if (!all(c("month", "year", "RET") %in% names(data))) next
  
  # Define predictor variables (all columns except RET, month, and year)
  x <- setdiff(names(data), c("RET", "month", "year"))
  
  # Loop through each unique month and calculate PLS R^2
  for (month in unique(data$month)) {
    monthly_data <- data[data$month == month, ]
    if (nrow(monthly_data) < 2) next
    
    predictors <- as.matrix(monthly_data[, x])
    response <- monthly_data$RET
    
    # Partial Least Squares Regression without cross-validation
    pls_model <- plsr(response ~ predictors, ncomp = 5)
    pls_r2 <- 1 - sum((response - predict(pls_model, predictors)[,,5])^2) / sum((response - mean(response))^2)
    
    # Store the R^2 and the count of observations for weighting
    monthly_pls_r2_list[[paste0(file_path, "_month_", month)]] <- pls_r2
    monthly_counts[[paste0(file_path, "_month_", month)]] <- nrow(monthly_data)
  }
  
  # Loop through each unique year and calculate PLS R^2
  for (year in unique(data$year)) {
    annual_data <- data[data$year == year, ]
    if (nrow(annual_data) < 2) next
    
    predictors <- as.matrix(annual_data[, x])
    response <- annual_data$RET
    
    # Partial Least Squares Regression without cross-validation
    pls_model <- plsr(response ~ predictors, ncomp = 5)
    pls_r2 <- 1 - sum((response - predict(pls_model, predictors)[,,5])^2) / sum((response - mean(response))^2)
    
    # Store the R^2 and the count of observations for weighting
    annual_pls_r2_list[[paste0(file_path, "_year_", year)]] <- pls_r2
    annual_counts[[paste0(file_path, "_year_", year)]] <- nrow(annual_data)
  }
}

# Calculate weighted monthly and annual R^2 for PLS
overall_monthly_pls_r2 <- sum(unlist(monthly_pls_r2_list) * unlist(monthly_counts)) / sum(unlist(monthly_counts))
print(paste("Overall Monthly PLS R^2:", overall_monthly_pls_r2))

overall_annual_pls_r2 <- sum(unlist(annual_pls_r2_list) * unlist(annual_counts)) / sum(unlist(annual_counts))
print(paste("Overall Annual PLS R^2:", overall_annual_pls_r2))

```
PCR
```{r}
# Load necessary libraries
library(arrow)
library(pls)

# Specify the current directory containing Parquet files
file_paths <- list.files(path = "./", pattern = "\\.parquet$", full.names = TRUE)

# Initialize lists to store R^2 values and observation counts for each month and year
monthly_pcr_r2_list <- list()
monthly_counts <- list()
annual_pcr_r2_list <- list()
annual_counts <- list()

# Loop through each file, process data, and store results
for (file_path in file_paths) {
  
  # Load data for the current file
  data <- read_parquet(file_path)
  
  # Check for required columns
  if (!all(c("month", "year", "RET") %in% names(data))) next
  
  # Define predictor variables (all columns except RET, month, and year)
  x <- setdiff(names(data), c("RET", "month", "year"))
  
  # Loop through each unique month and calculate PCR R^2
  for (month in unique(data$month)) {
    monthly_data <- data[data$month == month, ]
    if (nrow(monthly_data) < 2) next
    
    predictors <- as.matrix(monthly_data[, x])
    response <- monthly_data$RET
    
    # Principal Component Regression without cross-validation
    pcr_model <- pcr(response ~ predictors, ncomp = 5)
    pcr_r2 <- 1 - sum((response - predict(pcr_model, predictors)[,,5])^2) / sum((response - mean(response))^2)
    
    # Store the R^2 and the count of observations for weighting
    monthly_pcr_r2_list[[paste0(file_path, "_month_", month)]] <- pcr_r2
    monthly_counts[[paste0(file_path, "_month_", month)]] <- nrow(monthly_data)
  }
  
  # Loop through each unique year and calculate PCR R^2
  for (year in unique(data$year)) {
    annual_data <- data[data$year == year, ]
    if (nrow(annual_data) < 2) next
    
    predictors <- as.matrix(annual_data[, x])
    response <- annual_data$RET
    
    # Principal Component Regression without cross-validation
    pcr_model <- pcr(response ~ predictors, ncomp = 5)
    pcr_r2 <- 1 - sum((response - predict(pcr_model, predictors)[,,5])^2) / sum((response - mean(response))^2)
    
    # Store the R^2 and the count of observations for weighting
    annual_pcr_r2_list[[paste0(file_path, "_year_", year)]] <- pcr_r2
    annual_counts[[paste0(file_path, "_year_", year)]] <- nrow(annual_data)
  }
}

# Calculate weighted monthly and annual R^2 for PCR
overall_monthly_pcr_r2 <- sum(unlist(monthly_pcr_r2_list) * unlist(monthly_counts)) / sum(unlist(monthly_counts))
print(paste("Overall Monthly PCR R^2:", overall_monthly_pcr_r2))

overall_annual_pcr_r2 <- sum(unlist(annual_pcr_r2_list) * unlist(annual_counts)) / sum(unlist(annual_counts))
print(paste("Overall Annual PCR R^2:", overall_annual_pcr_r2))

```

importance of covariate top 10 with elastic net +H
```{r}
# Load necessary libraries
library(h2o)
library(arrow)
h2o.init()

# Specify the directory containing Parquet files
file_paths <- list.files(path = "./", pattern = "\\.parquet$", full.names = TRUE)

# Initialize list to store variable importance from each model
importance_list <- list()
counts <- 0

# Loop through each file, train model, and store variable importance
for (file_path in file_paths) {
  
  # Load data for the current file
  data <- read_parquet(file_path)
  h2o_data <- as.h2o(data)
  
  # Define response and predictor variables
  y <- "RET"
  x <- setdiff(names(data), y)
  
  # Train Elastic Net model on current subset
  model <- h2o.glm(x = x, y = y, training_frame = h2o_data, 
                   family = "gaussian",             # For regression
                   alpha = 0.5,                     # Elastic Net mixing parameter
                   lambda_search = TRUE)            # Enable automatic lambda tuning
  
  # Get variable importance and store it
  importance <- as.data.frame(h2o.varimp(model))
  importance_list[[file_path]] <- importance
  
  # Count the number of models (for averaging later)
  counts <- counts + 1
  
  # Clean up to free memory
  h2o.rm(h2o_data)
}

# Aggregate variable importance by averaging across models
importance_df <- Reduce(function(x, y) merge(x, y, by = "variable", all = TRUE), importance_list)
importance_df[is.na(importance_df)] <- 0  # Replace NAs with 0 for averaging
importance_df$average_importance <- rowMeans(importance_df[, -1])

# Sort by average importance and select the top 10 variables
top_10_importance <- importance_df[order(-importance_df$average_importance), ][1:10, c("variable", "average_importance")]

# Print top 10 most important features
print(top_10_importance)

# Shut down h2o
h2o.shutdown(prompt = FALSE)

# Load ggplot2 library for plotting
library(ggplot2)

# Exclude "month" and "sic_x35" from the data frame
filtered_importance <- top_10_importance[!top_10_importance$variable %in% c("month"), ]

# Plot the filtered top importance features
ggplot(filtered_importance, aes(x = reorder(variable, average_importance), y = average_importance)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +  # Flip coordinates to make it horizontal
  labs(title = "Top Feature Importance Elastice net", x = "Feature", y = "Average Importance") +
  theme_minimal()

```

importance of covariate top 10 with GLM +H
```{r}
# Load necessary libraries
library(h2o)
library(arrow)
h2o.init()

# Use "./" to specify the current directory containing Parquet files
file_paths <- list.files(path = "./", pattern = "\\.parquet$", full.names = TRUE)

# Initialize list to store variable importance from each model
importance_list <- list()
counts <- 0

# Loop through each file, process data, and store variable importance
for (file_path in file_paths) {
  
  # Load data for the current file
  data <- read_parquet(file_path)
  
  # Upload data to the h2o cluster
  h2o_data <- as.h2o(data)
  
  # Define response and predictor variables
  y <- "RET"
  x <- setdiff(names(data), y)  # All columns except RET as predictors
  
  # Train GLM with group lasso
  model <- h2o.glm(x = x, y = y, training_frame = h2o_data,
                   family = "gaussian",       # For linear regression
                   alpha = 1,                 # L1 penalty for group lasso
                   lambda_search = TRUE)      # Automatically search for the best lambda
  
  # Get variable importance and store it
  importance <- as.data.frame(h2o.varimp(model))
  importance_list[[file_path]] <- importance
  
  # Count the number of models (for averaging later)
  counts <- counts + 1
  
  # Clean up to free memory
  h2o.rm(h2o_data)
}

# Aggregate variable importance by averaging across models
importance_df <- Reduce(function(x, y) merge(x, y, by = "variable", all = TRUE), importance_list)
importance_df[is.na(importance_df)] <- 0  # Replace NAs with 0 for averaging
importance_df$average_importance <- rowMeans(importance_df[, -1])

# Sort by average importance and select the top 10 variables
top_10_importance <- importance_df[order(-importance_df$average_importance), ][1:10, c("variable", "average_importance")]

# Print top 10 most important features
print(top_10_importance)

# Shut down h2o
h2o.shutdown(prompt = FALSE)

# Load ggplot2 library for plotting
library(ggplot2)

# Exclude "month" and "sic_x35" from the data frame
filtered_importance <- top_10_importance[!top_10_importance$variable %in% c("month", "sic_x35"), ]

# Plot the filtered top importance features
ggplot(filtered_importance, aes(x = reorder(variable, average_importance), y = average_importance)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +  # Flip coordinates to make it horizontal
  labs(title = "Top Feature Importance GLM", x = "Feature", y = "Average Importance") +
  theme_minimal()


```


